Challenges and Solutions of Developing and Implementing a Revolutionary Novel Desktop-as-a-Service

### 2024-04-22 paper.tex
Some small fixes

>>>>

While developing the novel DaaS platform, we faced multiple obstacles and challenges. Each one these issues belong to one the four categories compatibility, performance, stability and usability. This section presents the issues we were confronted with and, the possible approaches we analyzed and the solutions we chose.
